\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-06-26 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

\medskip
Numerical simulations \citep[based on lab experiments due to][]{evans_1994,dawe_2008} were conducted to demonstrates the model capability to capture viscous crossflow in immiscible displacement in heterogeneous porous media. The 2D domain, shown in Fig.~\ref{fem_cv_represent_a}, is $4$ $\times$ $2$ unit-length (aspect ratio of $2$) and fully saturated with fluid 2 ({\it VR}=1). Fluid 1 is injected from the left-hand side of the domain with constant velocity of $u=1$. Boundary conditions also includes no-flux across upper and lower boundaries. The domain consists of four regions in which each quarter is represented by a permeability value, Fig.~\ref{fem_cv_represent_a}(a).

>>>>

\medskip
Numerical simulations \citep[based on lab experiments due to][]{evans_1994,dawe_2008} were conducted to demonstrates the model capability to capture viscous crossflow in immiscible displacement in heterogeneous porous media. The 2D domain, shown in Fig.~\ref{fem_cv_represent_a}, is $4$ $\times$ $2$ unit-length and fully saturated with fluid 2 ({\it VR}=1). Fluid 1 is injected from the left-hand side of the domain with constant velocity of $u=1$. Boundary conditions also include no-flux across upper and lower borders. The domain consists of four regions in which each quarter is represented by a permeability value, Fig.~\ref{fem_cv_represent_a}(a).
